Exploring the Soil Microbiome coupling with the Crete island Data Cube

### 2024-04-04 manuscript.tex
intro first draft ready

Soil ecosystem functioning

Interactomes have been characterised as a driver of community composition soil
functioning \cite{GUSEVA2022108604}.
Still the challenges to infer actual microbial interactions remain \cite{Faust2021}.

Integration of prior knowledge and

UN and EU soil goals for the 2030

>>>>

Disentagling the soil ecosystem functioning requires an holistic and 
multidisciplinary approach \cite{vogel2022}. The integration of the afformentioned
data is needed to understand the biogeochemical cycles along with biodiversity interactomes 
that have been characterised as a driver of community composition soil
functioning \cite{GUSEVA2022108604}.
Regarding the latter there are still big challenges to infer actual microbial
interactions remain \cite{Faust2021}. All this work is needed in order to meet
UN and EU soil goals for the 2030 and 2050 for healthy soils \cite{LAL2021e00398}.
